Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes

### 2018-11-19 Ben_Manuscripts/structure_paper/Final_Draft.tex
Fixes to references

  We quantified the movement of the tails during our simulations by calculating the 
  autocorrelation function of the dihedral angle formed around the bond between the 
  head groups and the ether oxygens which attach the tails to the head group 
  (see Figure \ref{S-fig:dihedrals} of the SI). We exclude the dihedral from the middle tail 
  since it is fundamentally different than the two symmetric outside tails. We 
  limited these studies to the sandwiched configuration for simplicity.

@@

  \label{modification:conductivity}
  The calculated value of ionic conductivity is 5 times higher than experiment 
  likely because we simulated infinitely long, aligned pores and because our 
  model over-predicts the diffusivity of sodium. The ionic conductivity measurement 
  to which we are comparing was done with an \SI{80}{\micro\metre}-thick film, 
  nearly 10,000 times thicker than our simulated
  system. The thick film is likely imperfectly aligned and has defects leading to
  non-contiguous pores. It has been shown that there is a large dependence of 
  ionic conductivity on the alignment of the pores. The ionic conductivity of an
  isotropically aligned film is ca. 85 times lower than that of the nearly aligned
  film to which we are comparing~\cite{feng_scalable_2014}. Additionally,
  the parameters for sodium ions in this system exhibit bulk water diffusion 
  coefficients that are two times greater than experiment ~\cite{bruce_molecular_2002}.
  We cannot definitively say exactly how this ratio changes in the confined LLC pore
  environment, but it is likely that sodium diffuses faster in our system which
  contributes to a higher ionic conductivity than experiment.

  We hypothesize that a 
  thin, perfectly aligned film would have a value of ionic conductivity in closer
  agreement with our model.

>>>>

  We quantified the movement of the tails during our simulations by calculating the 
  autocorrelation function of the dihedral angle formed around the bond between the 
  head groups and the ether oxygens which attach the tails to the head group 
  (see Figure \ref{S-fig:dihedral} of the SI). We exclude the dihedral from the middle tail 
  since it is fundamentally different than the two symmetric outside tails. We 
  limited these studies to the sandwiched configuration for simplicity.

@@

  \label{modification:conductivity}
  The calculated value of ionic conductivity is 5 times higher than experiment 
  likely because we simulated infinitely long, aligned pores and because our 
  model over-predicts the diffusivity of sodium. The ionic conductivity measurement 
  to which we are comparing was done with an \SI{80}{\micro\metre}-thick film, 
  nearly 10,000 times thicker than our simulated
  system. The thick film is likely imperfectly aligned and has defects leading to
  non-contiguous pores. It has been shown that there is a large dependence of 
  ionic conductivity on the alignment of the pores. The ionic conductivity of an
  isotropically aligned film is ca. 85 times lower than that of the nearly aligned
  film to which we are comparing~\cite{feng_scalable_2014}. Additionally, sodium 
  ions parameterized with AMBER parameters exhibit bulk water diffusion coefficients
  that are two times greater than experiment\cite{bruce_molecular_2002}. We cannot
  definitively say how this ratio changes in the confined LLC pore environment,
  but it is likely that sodium diffuses faster than experiment in our system which
  contributes to a higher ionic conductivity.

%  We hypothesize that a 
%  thin, perfectly aligned film would have a value of ionic conductivity in closer
%  agreement with our model.

### 2018-11-19 Ben_Manuscripts/structure_paper/supporting_information.tex
Fixes to references

  The system size, in the $z$-direction, does not significantly alter $g(z)$.
  In Figure~\ref{S-fig:correlation}, oscillations do not fully decay, so a taller
  system may be necessary to fully capture the correlation function. We therefore
  equilibrated a sandwiched system with twice as many monomers per column so that
  the system size doubled in the $z$-direction. The correlation length increases
  modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. However, visually, the
  correlation functions are nearly identical and oscillatory behavior persists
  throughout $g(z)$ in both cases (See Figure \ref{S-fig:z_correlation_overlay}).

  It seems likely that the discrepancy between the shape and intensity of
  R-$\pi$ generated from our simulations versus experiment is primarily due to
  highly correlated columns in our highly symmetric initial configurations.
  If the columns were uncorrelated, $g(z)$ of the ordered sandwiched system 
  would very closely resemble Figure~\ref{S-fig:z_correlation_sandwich} when we 
  average all $z$-slices of the 3D correlation function. Contributions to
  $g(z)$ from head groups in other columns within the same pore, and with head
  groups in different pores would cancel out. However, when we include all 
  $z$-slices in $g(z)$ for our system, rather than restricting it to those 
  $z$-slices within 2.1~\AA~of the center of the correlation function 
  (see Section~\ref{M-section:correlation_length}), $g(z)$ shows oscillatory 
  behavior and its correlation length nearly triples to 12.4 $\pm$ 0.7 \AA.
  (Figure~\ref{fig:z_correlation_fullbox}). The peaks of $g(z)$ are actually 
  reinforced by head groups in neighboring columns which is not expected
  in a system where columns act independently.

@@

  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
  cross-section of R-$\pi$ to, somewhat counterintuitively, decrease. Using a
  system with uncorrelated columns, we modified the disorder in both the $r$ and
  $\theta$ directions by multiplying their values by a factor of 0.5 and 2
  (Figure~\ref{fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
  by 88\%. When we double the noise, the FWHM decreases by 51\%. As we have fit
  the data in Figure~\ref{fig:sim_rsection_fit}, the FWHM of R-$\pi$ agrees well
  with experiment, meaning the quenched configuration contains about the right
  amount of disorder on the $xy$ plane. However, the relatively low quality of
  the fit implies that the FWHM of a fixed Lorentzian fit to data from a single
  simulation might not be the best comparison to experiment and that some form of
  initial configuration dependence causes extra structure.

>>>>

  The system size, in the $z$-direction, does not significantly alter $g(z)$.
  In Figure~\ref{fig:correlation}, oscillations do not fully decay, so a taller
  system may be necessary to fully capture the correlation function. We therefore
  equilibrated a sandwiched system with twice as many monomers per column so that
  the system size doubled in the $z$-direction. The correlation length increases
  modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. However, visually, the
  correlation functions are nearly identical and oscillatory behavior persists
  throughout $g(z)$ in both cases (See Figure \ref{fig:z_correlation_overlay}).

  It seems likely that the discrepancy between the shape and intensity of
  R-$\pi$ generated from our simulations versus experiment is primarily due to
  highly correlated columns in our highly symmetric initial configurations.
  If the columns were uncorrelated, $g(z)$ of the ordered sandwiched system 
  would very closely resemble Figure~\ref{fig:z_correlation_sandwich} when we 
  average all $z$-slices of the 3D correlation function. Contributions to
  $g(z)$ from head groups in other columns within the same pore, and with head
  groups in different pores would cancel out. However, when we include all 
  $z$-slices in $g(z)$ for our system, rather than restricting it to those 
  $z$-slices within 2.1~\AA~of the center of the correlation function 
  (see Section~\ref{M-section:correlation_length}), $g(z)$ shows oscillatory 
  behavior and its correlation length nearly triples to 12.4 $\pm$ 0.7 \AA.
  (Figure~\ref{fig:z_correlation_fullbox}). The peaks of $g(z)$ are actually 
  reinforced by head groups in neighboring columns which is not expected
  in a system where columns act independently.

@@

  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
  cross-section of R-$\pi$ to, somewhat counterintuitively, decrease. Using a
  system with uncorrelated columns, we modified the disorder in both the $r$ and
  $\theta$ directions by multiplying their values by a factor of 0.5 and 2
  (Figure~\ref{fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
  by 88\%. When we double the noise, the FWHM decreases by 51\%. As we have fit
  the data in Figure~\ref{M-fig:sim_rsection_fit}, the FWHM of R-$\pi$ agrees well
  with experiment, meaning the quenched configuration contains about the right
  amount of disorder on the $xy$ plane. However, the relatively low quality of
  the fit implies that the FWHM of a fixed Lorentzian fit to data from a single
  simulation might not be the best comparison to experiment and that some form of
  initial configuration dependence causes extra structure.
